---
title: Contents
description: |
  Course materials including presentations (slides) and practical
  exercises (labs)
toc: false
date: ""
sidebar: false
format:
  html:
    number-sections: false
execute:
  freeze: false
filter:
  - fontawesome
---

{{< include _rinit.qmd >}}

```{r }
#| label: r-make-contents
#| echo: false
#| eval: true
#| cache: false
smkd <- s %>%
  tidyr::fill(date, .direction = "down") %>%
  # create links
  dplyr::mutate(link_lab_jlite = ifelse(
    is.na(link_lab), NA,
    gsub(
      ",", "",
      gsub(
        "([^,]+)",
        paste0(
          " **[{{< fa brands firefox-browser >}}](",
          server, "\\1)**"
        ),
        link_lab
      )
    )
  )) %>%
  dplyr::mutate(link_lab_colab = ifelse(
    is.na(link_lab), NA,
    gsub(
      ",", "",
      gsub(
        "([^,]+)",
        paste0(
          " **[{{< fa brands google >}}](",
          colabhost, "\\1)**"
        ),
        link_lab
      )
    )
  )) %>%
  dplyr::mutate(link_slide = ifelse(
    is.na(link_slide), NA,
    paste0("**[{{< fa file-powerpoint >}}](", link_slide, ")**")
    )) %>%
  dplyr::mutate(material = "") %>%
  dplyr::mutate(material = ifelse(is.na(link_slide),
                                  material,
                                  paste(material, link_slide)
                                  )) %>%
  dplyr::mutate(material = ifelse(is.na(link_lab_jlite),
                                  material,
                                  paste(material, link_lab_jlite)
                                  )) %>%
  dplyr::mutate(material = ifelse(is.na(link_lab_colab),
                                  material,
                                  paste(material, link_lab_colab)
                                  ))
```                                  
  <!-- dplyr::mutate(title = ifelse(is.na(link_slide), -->
  <!--   title, -->
  <!--   paste(title, link_slide) -->
  <!-- )) %>% -->
  <!-- dplyr::mutate(title = ifelse(is.na(link_lab_jlite), -->
  <!--   title, -->
  <!--   paste(title, link_lab_jlite) -->
  <!-- )) %>% -->
  <!-- dplyr::mutate(title = ifelse(is.na(link_lab_colab), -->
  <!--   title, -->
  <!--   paste(title, link_lab_colab) -->
  <!-- )) -->


::: {.callout-note}

The contents are being updated.

:::

You can access exercise content in several ways:

1. click on the relevant icon links in the table below (see table
   legend for explanation)
2. clone the repo and install requirements (you may want to do this in
   a dedicated [conda environment](https://docs.anaconda.com/)):
   - (OPTIONAL): `conda create -n garg python=3.12`
   - `git clone https://github.com/ebp-nor/GARG.git`
   - `cd GARG && python -m pip install .`
3. you can access all online JupyterLite content by navigating to the
   file browser view (<https://ebp-nor.github.io/GARG/jlite/tree>) or
   the JupyterLab view (<https://ebp-nor.github.io/GARG/jlite/lab>)
   

:::{.contents-table .column-body-outset}

```{r }
#| label: r-contents-table-markdown-out
#| echo: false
#| eval: true
#| results: asis
cnames <- c("Date", "Title", "Topic", "Material", "Presenter")
tab <- smkd %>%
  dplyr::filter(title != "") %>%
  dplyr::filter(type %in% c("Talk", "Lab", "Seminar")) %>%
  dplyr::select(c("date", "title", "body", "material", "instructor")) %>%
  dplyr::mutate_all(~ ifelse(is.na(.), "", .)) %>%
  setNames(cnames[1:ncol(.)]) %>%
  dplyr::distinct()

tabby <- by(tab, tab$Date, function(x) {
  x
})

contents <- do.call(
  "rbind",
  lapply(names(tabby), function(date) {
    x <- tabby[[date]][, 2:5]
    new_row <- tibble::tibble(
      Title = paste0("[**", date, "**]{.badge .badge-secondary}"),
      Topic = "",
      Material = "",
      Presenter = ""
    )
    x <- rbind(new_row, x)
    x
  })
)

cat(
  print(kable(contents, format = "pipe", escape = FALSE, row.names = FALSE)),
  "\n\n: {.hover .condensed .responsive tbl-colwidths=\"[30, 50, 20]\"}\n\n"
)
```

:::

<!-- marker legend -->
<p class="small" style="margin-top:20px;">
<span>
<span style="margin-left:6px; margin-right:6px;">
{{< fa file-powerpoint >}} Slides </span>
<span style="margin-left:6px; margin-right:6px;">
{{< fa brands google-drive >}} Slides (Google Drive) </span>
<span style="margin-left:6px; margin-right:6px;">
{{< fa brands firefox-browser >}} Exercises (JupyterLite) </span>
<span style="margin-left:6px; margin-right:6px;">
{{< fa brands google >}} Exercises (Google CoLab) </span>
</span>
</p>
